\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{rotating}
\newcommand{\tab}{\hspace*{2em}}
\newcommand{\tabb}{\hspace*{4em}}
\newcommand{\tabbb}{\hspace*{6em}}
\newcommand{\tabbbb}{\hspace*{8em}}
\newcommand{\tabbbbb}{\hspace*{10em}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\setlength{\parindent}{0in} 
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Dynamic Programming Problems\\
	10.05.2011
	\end{flushright}
	21.	The input to this problem is a sequence of $n$ points $p_1, \ldots, p_n$ in the Euclidean plane. You are to find
		the shortest routes for two taxis to service these requests in order. Let us be more specific. The two
		taxis start at the origin. If a taxi visits a point $p_i$ before $p_j$ then it must be the case that $i < j$. (Stop
		and think about what this last sentence means.) Each point must be visited by at least one of the two
		taxis. The cost of a routing is just the total distance traveled by the first taxi plus the total distance
		traveled by the second taxi. Design an efficient algorithm to find the minimum cost routing.\\
		\\
		Tree description:\\
		\\
		The tree nodes are indexed by $[taxi~1$'$s~position,~taxi~2$'$s~position]$. This scheme brings the total
		space requirement to $O(n^2)$.\\
		\\
		Pruning Rule:\\
		1) For all values the same level with equal indices, prune all but the shortest. There will be $2*n$
		values at level $n$.\\
		\\
		Initialization: \\
		$A[*,*] = \infty$\\
		$A[p_1,O] = \norm{O+p_1}$, where O is the origin\\
		\\
		For i = 1 to n-1:\\
		\tab For j = 0 to i-1:\\
		\tabb $A[i+1,j] = A[j,i+1] = min( A[j,i+1], A[i+1,j], A[i,j] + \norm{p_i + p_{i+1}} )$\\
		\tabb $A[i+1,i] = A[i,i+1] = min( A[i,i+1], A[i+1,i], A[i,j] + \norm{p_j + p_{i+1}} )$\\
		\\
		The minimum-length path will be in row $A[*,n]$.
		
\end{document}
