\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{rotating}
\newcommand{\tab}{\hspace*{2em}}
\newcommand{\tabb}{\hspace*{4em}}
\newcommand{\tabbb}{\hspace*{6em}}
\newcommand{\tabbbb}{\hspace*{8em}}
\newcommand{\tabbbbb}{\hspace*{10em}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\setlength{\parindent}{0in} 
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Dynamic Programming Problems\\
	10.19.2011
	\end{flushright}
		7. Show that if one of the following three problems has a polynomial time algorithm then they all do.
		\begin{itemize}
		\item The input is two undirected graphs $G$ and $H$. The problem is to determine if the graphs are
		isomorphic.
		\item The input is two directed graphs $G$ and $H$. The problem is to determine if the graphs are
		isomorphic.
		\item The input is two undirected graphs $G$ and $H$, and an integer $k$. The problem is to determine if
		\end{itemize}
		the graphs are isomorphic and all the vertices in each graph have degree $k$.
		Intuitively, two graphs are isomorphic if on can name/label the vertices so that the graphs are identical.
		More formally, two undirected graphs $G$ and $H$ are isomorphic if there is a bijection $f$ from the vertices
		of $G$ to the vertices of $H$ such that $(v, w)$ is an edge in $G$ if and only if $(f (v), f (w))$ is an edge in $G$.
		More formally, two directed graphs $G$ and $H$ are isomorphic if there is a bijection $f$ from the vertices
		of $G$ to the vertices of $H$ such that $(v, w)$ is a directed edge in $G$ if and only if $(f (v), f (w))$ is a directed
		edge in $G$. The degree of a vertex is the number of edges incident to that vertex.
		\\
		\\
		9. The input to the Hamiltonian Cycle Problem is an undirected graph $G$. The problem is to find a
		Hamiltonian cycle, if one exists. A Hamiltonian cycle is a simple cycle that spans $G$. Show that the
		Hamiltonian cycle problem is self reducible. That it, show that if there is a polynomial time algorithm
		that determines whether a graph has a Hamiltonian cycle, then there is a polynomial time algorithm
		to find Hamiltonian cycles.
		\\
		\\
		Hamiltonian Cycle Optimization $\leq$ Hamiltonian Cycle Decision.\\
		\\
		program hamiltonian cycle optimization:\\
		\tab read $G$\\
		\tab If $G$ has a hamiltonian cycle: \emph{call to hamiltonian cycle}\\ 
		\tabb for each node, $n$ in $G$:\\
		\tabbb $G^\prime = G - n$\\
		\tabbb If $G^\prime$ has a hamiltonian cycle:\\
		\tabbbb $G = G^\prime$\\
		\tab output $G$
		\\
		\\
		13. Show that the following problem is $NP$-hard:\\
		INPUT: A graph $G$. Let $n$ be the number of vertices in $G$.\\
		OUTPUT: 1 if $G$ contains a simple cycle with $\sqrt{n}$ edges, and 0 otherwise.\\
		Use the fact the the following problem is $NP$-hard:\\
		INPUT: A graph $G$.\\
		OUTPUT: 1 if $G$ contains a simple cycle that spans $G$, and 0 otherwise.\\
		Note that a cycle is simple if it doesn’t visit any vertex more than once. A cycle spans $G$ if every
		vertex is included in the cycle.\\
		\\
		Simple Cycle (SC) $\leq$ Simple Cycle Square Root (SCSR)\\
		\\
		program SC:\\
		\tab read $G$\\
		\tab $n$ = number verticies in $G$\\
		\tab $H$ = $n$ disjoint copies of $G$\\
		\tab output SCSR($H$)\\
		\\
		We've created a graph, $H$, with $n^2$ vertices. Since the copies of $G$ are disjoint the only case in which a simple cycle of 
		length $\sqrt{n}$ will appear is when there is a simple cycle spanning $G$.
\end{document}
