\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{rotating}
\newcommand{\tab}{\hspace*{2em}}
\newcommand{\tabb}{\hspace*{4em}}
\newcommand{\tabbb}{\hspace*{6em}}
\newcommand{\tabbbb}{\hspace*{8em}}
\newcommand{\tabbbbb}{\hspace*{10em}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\setlength{\parindent}{0in} 
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Dynamic Programming Problems\\
	10.28.2011
	\end{flushright}
	11.  Show that the Vertex Cover Problem is self-reducible. The decision problem is to take a graph $G$ and
an integer $k$ and decide if $G$ has a vertex cover of size $k$ or not.  The optimization problem takes a
graph $G$, and returns a smallest vertex cover in $G$.  So you must show that if the decision problem
has a polynomial time algorithm then the optimization problem also has a polynomial time algorithm.
Recall that a vertex cover is a collection $S$ of vertices with the property that every edge is incident to
a vertex in $S$.\\
    \\
	\textbf{VERTEXCOVER-OPT} $\leq$ \textbf{VERTEXCOVER-DEC}\\
	\\
	Program VERTEXCOVER-OPT:\\
	\tab Read graph $G$, integer $k$.\\
	\tab \emph{First, find the smallest size of the smallest vertex cover.}\\
	\tab For $k$ = 1 to $n$:\\
	\tabb If VERTEXCOVER-DEC($G$,$k$) returns true:\\
	\tabbb size $s$ = $k$.\\
	\tabbb End for-loop.\\
	\tab \emph{Next, find the actual cover by removing the vertices NOT in the cover}\\
	\tab For each vertex $v$ in $G$:\\
	\tab  $G^\prime$ = $G$ - $v$\\
	\tabb If VERTEXCOVER-DEC($G^\prime$, $s$) returns true:\\
	\tabbb $G$ = $G^\prime$.\\
	\tab \emph{G is the graph containing only the smallest cover.}\\
	\tab Return $G$.\\
    \\
	\newpage
	14.  Consider the problem where the input is a collection of linear inequalities.  For example, the input
might look like $3x-2y \leq 3$ and $2x-3y \geq 9$. The problem is to determine if there is an integer solution
that simultaneously satisfies all the inequalities. Show that this problem is  NP-hard using the fact that
it is NP-hard to determine if a Boolean formula in conjunctive normal form is satisfiable.
	\\
	\\
	\textbf{CNF-SAT} $\leq$ \textbf{LINEAR-INEQ}\\
	\\
	Program CNF-SAT:\\
	\tab Read formula $F$\\
	\tab $F^\prime$ = ConstructEquation($F$)\\ 
	\tab Output	LINEAR-INEQ($F^\prime$)\\
	\\
	ConstructEquation($F$):\\
	Separate the CNF formula by the conjuncts to create $n$ separate statements.\\
	For each of these $n$ statements constuct one side of the inequality by 
	summing each of the literals (now variables) and multiplying those variables by
	-1 that are the negated literals. Make this sum $\leq -1*(the~number~of~literals) + 1$.\\
	\\
	Ex: $x \vee y \vee \neg z$ becomes $x + y -z \leq -2$
		
	16.  The input to the three coloring problem is a graph $G$, and the problem is to decide whether the vertices
of $G$ can be colored with three colors such that no pair of adjacent vertices are colored the same color.
The input to the four coloring problem is a graph $G$, and the problem is to decide whether the vertices
of $G$ can be colored with four colors such that no pair of adjacent vertices are colored the same color.
Show by reduction that if the four coloring problem has a polynomial time algorithm then so does the
three coloring problem. 
\end{document}
