\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{rotating}
\newcommand{\tab}{\hspace*{2em}}
\newcommand{\tabb}{\hspace*{4em}}
\newcommand{\tabbb}{\hspace*{6em}}
\newcommand{\tabbbb}{\hspace*{8em}}
\newcommand{\tabbbbb}{\hspace*{10em}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\setlength{\parindent}{0in} 
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Reduction and Parallel Problems\\
	10.31.2011
	\end{flushright}
	17. Consider the following problem. The input is an undirected graph $G$ and an integer $k$. The problem
	is to determine if $G$ contains a clique of size $k$ \textbf{AND} an independent set of size $k$. Recall that a
	clique is a collection of mutually adjacent vertices, and an independent set is a collection of mutually
	nonadjacent vertices. Show by reduction that if this problem has a polynomial time algorithm then
	the clique problem has a polynomial time algorithm.
	\\
	\\
	18. Consider the following problem. The input is an undirected graph $G$ and an integer $k$. The problem
	is to determine if $G$ contains a clique of size $k$ \textbf{OR} an independent set of size $k$. Show by reduction
	that if this problem has a polynomial time algorithm then the clique problem has a polynomial time
	algorithm.
	\\
	\\
	22. Consider the following problem. The input is a graph $G = (V, E)$, a subset $R$ of vertices of $G$, and a
	positive integer $k$. The problem is to determine if there is a subset $U$ of $V$ such that
	\begin{enumerate}
		\item All the vertices in $R$ are contained in $U$, and
		\item the number of vertices in $U$ is at most $k$, and
		\item for every pair of vertices $x$ and $y$ in $R$, one can walk from $x$ to $y$ in $G$ only traversing vertices that
		are in $U$.
	\end{enumerate}
	Show that this problem is NP-hard using a reduction from Vertex Cover. Recall that the input for the
	vertex cover problem is a graph $H$ and an integer $\ell$, and the problem is to determine whether $H$ has a
	vertex cover of size $\ell$ or not. A vertex cover $S$ is a collection of vertices with the property that every
	edge is incident on at least one vertex in $S$.
		\\
	\\
	1. Consider the problem of computing the AND of $n$ bits.
	\begin{enumerate}
		\item Give an algorithm that runs in time O(log $n$) using n processors on an EREW PRAM. What is
		the endciency of this algorithm?
		\item Give an algorithm that runs in time O(log $n$) using n= log n processors on an EREW PRAM.
		What is the endciency of this algorithm?
		\item Give an algorithm that runs in time O(1) using n processors on a CRCW PRAM.
	\end{enumerate}
\end{document}
