\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\newcommand{\tab}{\hspace*{2em}}
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Greedy Algorithm Problems\\
	9.11.2011
	\end{flushright}
	\noindent
	9.  The input to this problem consists of an ordered list of $n$ words. The length of the $i$th word is $w_{i}$, that
			is the ith word takes up $w_{i}$ spaces.  (For simplicity assume that there are no spaces between words.)
			The goal is to break this ordered list of words into lines, this is called a layout. Note that you can not
			reorder the words.  The length of a line is the sum of the lengths of the words on that line. The ideal
			line length is $L$. No line may be longer than $L$, although it may be shorter.  The penalty for having a
			line of length $K$ is $L - K$. \textit{The total penalty is the \textbf{sum} of the line penalties}. The problem is to find a
			layout that minimizes the total penalty.\\
			Prove of disprove that the following greedy algorithm correctly solves this problem.
			
			\begin{verbatim}
			For i= 1 to n
			     Place the ith word on the current line if it fits
			      else place the ith word on a new line
			\end{verbatim}
			% answer here
			Prove that the greedy algorithm is correct.\\
			Proof: Assume $\exists$ input I $\ni$ GRE(I) $<$ OPT(I), let OPT be the optimal solution that agrees with greedy
			for the most steps, $k$.\\
			\\
			$GRE(I) = 
			\begin{array}{ccccc}
				w_{0} & w_{1} & \ldots & w_{k-1} & w_{k}\\
				w_{k+1} & w_{k+2} & \ldots & w_{n}\\  
			\end{array}\bigg\}, k = N L - \sum w$, where N is the numner of lines
			\\
			\\
			$OPT(I) = 
			\begin{array}{ccccc}
				w_{0} & w_{1} & \ldots & w_{k-1}\\
				w_{k} & w_{k+1} & \ldots & w_{n-1}\\
				w_{n}  
			\end{array}\bigg\}, k = N L - \sum w$\\
			Let the first point of disagreement be at point $k$. We can construct $OPT^{\prime}$ as the following.\\
			$OPT^{\prime}(I) = 
			\begin{array}{ccccc}
				w_{0} & w_{1} & \ldots & w_{k}\\
				w_{k+1} & w_{k+2} & \ldots & w_{n-1}\\
				w_{n}  
			\end{array}\bigg\}, k = N L - \sum w$\\
			\\
			At this point $k$ is non-increasing, so $OPT^{\prime} \geq OPT$, and we can construct $OPT^{\prime\prime}$ which
			will agree with greedy for an additional step.\\
			\\
			$OPT^{\prime\prime}(I) = 
			\begin{array}{ccccc}
				w_{0} & w_{1} & \ldots & w_{k}\\
				w_{k+1} & w_{k+2} & \ldots & w_{n}
			\end{array}\bigg\}, k = (N - 1) L - \sum w$\\
			\\	
			$OPT \leq OPT^{\prime} \leq OPT^{\prime\prime} \leq \ldots = GRE \bot$\\
			\\					 
	10. The input to this problem consists of an ordered list of $n$ words. The length of the $i$th word is $w_{i}$ , that
			is the $i$th word takes up $w_{i}$ spaces.  (For simplicity assume that there are no spaces between words.)
			The goal is to break this ordered list of words into lines, this is called a layout. Note that you can not
			reorder the words.  The length of a line is the sum of the lengths of the words on that line. The ideal
			line length is $L$. No line may be longer than $L$, although it may be shorter.  The penalty for having a
			line of length $K$ is $L - K$. The total penalty is the maximum of the line penalties. The problem is to
			find a layout that minimizes the total penalty.\\
			Prove of disprove that the following greedy algorithm correctly solves this problem.
			
			\begin{verbatim}
			For i= 1 to n
			     Place the ith word on the current line if it fits
			       else place the ith word on a new line
			\end{verbatim}
			%answer here
			\newpage
			\noindent
			Counter-exmaple:\\
			Consider the following input: $I$ = [2, 1, 1] and $L$ = 3,\\
			GRE(I) = $
			\begin{array}{ccc}
				2 & 1 & k = 0\\
				1 &   & k = 2\\
				  &   & max(k) = 2
			\end{array}$
			\\
			\\
			\\
			OPT(I) = $
			\begin{array}{ccc}
				2 &   & k = 1\\
				1 & 1 & k = 1\\
				  &   & max(k) = 1
			\end{array}$\\
			\\			
	13. Consider the following problem.\\
			INPUT: Positive integers $r_{1}, \ldots, r_{n}$ and $c_{1}, \ldots , c_{n}$.\\
			OUTPUT: An $n$ by $n$ matrix $A$ with 0/1 entries such that for all $i$ the sum of the $i$th row in $A$ is $r_{i}$
			and the sum of the $i$th column in $A$ is $c_{i}$, if such a matrix exists.\\
			Think of the problem this way.  You want to put pawns on an $n$ by $n$ chessboard so that the $i$th row
			has $r_{i}$ pawns and the $i$th column has $c_{i}$ pawns.\\
			Consider the following greedy algorithm that constructs $A$ row by row.  Assume that the first $i - 1$
			rows have been constructed. Let a $j$ be the number of 1’s in the $j$th column in the first $i - 1$ rows. Now
			the $r_{i}$ columns with with maximum $c_{j} - a_{j}$ are assigned 1’s in row $i$, and the rest of the columns are
			assigned 0’s. That is, the columns that still needs the most 1’s are given 1’s. Formally prove that this
			algorithm is correct.\\
			\\
			%answer here
	
\end{document}
	
	