\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{rotating}
\newcommand{\tab}{\hspace*{2em}}
\newcommand{\tabb}{\hspace*{4em}}
\newcommand{\tabbb}{\hspace*{6em}}
\newcommand{\tabbbb}{\hspace*{8em}}
\newcommand{\tabbbbb}{\hspace*{10em}}
\newcommand{\norm}[1]{\left|\left|#1\right|\right|}
\setlength{\parindent}{0in} 
\begin{document}
	\begin{flushright}
	Lindsey Bieda and Joe Frambach\\
	Reduction and Parallel Problems\\
	11.14.2011
	\end{flushright}

15. Give an algorithm for the minimum edit distance problem that runs in poly-log time on a CREW
PRAM with with a polynomial number of processors. Here poly-log means O($log^k n$) where $n$ is the
input size, and $k$ is some constant independent of the input size.\\
Recall that the input to this problem is a pair of strings $A = a_1 \ldots a_m$ and $B = b_1 \ldots b_n$. The goal is
to convert $A$ into $B$ as cheaply as possible. The rules are as follows. For a cost of 3 you can delete any
letter. For a cost of 4 you can insert a letter in any position. For a cost of 5 you can replace any letter
by any other letter.

\newpage
17. Design a parallel algorithm that finds the maximum number in a sequence $x_1, \ldots , x_n$ of (not necessarily
distinct) integers. Your algorithm should run in time O(log log $n$) on a CRCW PRAM with $n$ processors.\\
HINT: Recall that you can find the maximum of $k$ numbers in O(1) time with 
$\Omega(k^2)$ processors. Try divide and conquer into $\sqrt{n}$ subproblems.

\newpage
18. Design a parallel algorithm that finds the maximum number in a sequence $x_1, \ldots ,x_n$ of (not necessarily
distinct) integers in the range 1 to $n$. Your algorithm should run in constant time on a CRCW Priority
PRAM with $n$ processors. Note that it is important here that the $x_i$'s have restricted range. In a
CRCW priority PRAM, each processor has a unique positive integer identifier, and in the case of write
conflicts, the value written is the value that the processor with the lowest identifier is trying to write.\\
\\
ParFor $i$ = 1 to $n$:\\
\tab Existance[$x_i$] = 1\\
\\
ParFor $i$ = 1 to $n$:\\
\tab Write $n-i$ to Output if Existance[$x_i$]\\
\\
First we create an existance array to determine which numbers in the range of $1 \ldots n$ exist. Then we make use
of the Priority PRAM and write to the output the highest number that exists with the processor that has the lowest
identifier (that is writing).  
\newpage
20. Show that if there is an an algorithm for a particular problem that runs in time T ($n$, $p$) on a $p$
processor CRCW machine, then there is an algorithm for this problem that runs in time T ($n$, $p$) log p
on a $p$ processor EREW machine,\\
Hint: So you need to come up with an algorithm for the following problems:
\begin{enumerate}
	\item[(a)] At some particular time, some subcollection $P$ of processors want to read from a particular location
	$x$. The processors in $P$ do not know the identity, or even the number of processors in $P$. Yet the
	processors in $P$ need to work together to learn the value stored in location $x$ in time $O$(log $p$).
	\item[(b)] At some particular time, some subcollection $P$ of processors want to write a common value to
	a particular location $x$. The processors in $P$ do not know the identity, or even the number of
	processors in $P$. Yet the processor in $P$ need to work together to write the value to in location $x$
	in time $O$(log $p$).
\end{enumerate}


\end{document}
